|

### 2020-07-22 paper.Rmd
Playing with binned displays for Fig 1.

set.seed(2020)

@@

proj_points <- as_tibble(rbind(p3, p10, p100)) %>%
  add_column(p = c(rep(3, n), rep(10, n), rep(100, n)))

ggplot(proj_points, aes(x, y)) +
  geom_point(alpha=0.02) + 
  geom_density2d(bins = 7, contour_var = "ndensity") +
  coord_fixed() +
  theme_bw() +
  facet_wrap(~p, labeller = labeller(name = lbl)) +
  guides(color = FALSE) +
  theme(axis.title.x=element_blank(), axis.title.y=element_blank())

>>>>

set.seed(12345)

@@

proj_points <- as_tibble(rbind(p3, p10, p100)) %>%
  mutate(p = c(rep(3, n), rep(10, n), rep(100, n)))

ggplot(proj_points, aes(x, y)) +
  #geom_point(alpha=0.02) + 
  #geom_density2d(bins = 7, contour_var = "ndensity") +
  geom_hex(bins = 12, aes(fill=log(..count..))) +
  #geom_hex(bins = 12) +
  scale_fill_viridis_c() +
  coord_fixed() +
  theme_bw() +
  facet_wrap(~p, labeller = labeller(name = lbl)) +
  #guides(color = FALSE) +
  theme(axis.title.x=element_blank(), axis.title.y=element_blank())

### a radial binning
n <- 5
r_breaks <- seq(0, 1, length.out = n+1)
proj_points_rbin <- proj_points %>%
  mutate(r = sqrt(x^2 + y^2)) %>%
  mutate(bin = cut(r, r_breaks)) %>%
  mutate(bin_up = as.numeric( sub("[^,]*,([^]]*)\\]", "\\1", bin))) %>%
  group_by(p) %>%
  count(bin_up) %>%
  arrange(-bin_up)

ggplot(proj_points_rbin) +
  geom_circle(aes(x0= 0, y0=0, r = bin_up, fill=log(n))) +
  scale_fill_viridis_c() +
  facet_wrap(~p, labeller = labeller(name = lbl)) +
  coord_fixed() +
  theme_bw()
